\documentclass[10pt,twocolumn,letterpaper]{article}

\begin{document}

%%%%%%%%% TITLE
\title{Predicting a Film's Rating Utilizing Machine Learning}

\author{Joel Martinez\\
Texas State University\\
\and
Jose Garcia\\
Texas State University\\
\and
Kameron Bush\\
Texas State University\\
}
\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   We present a program that will utilize existing data on films that have been released in order to predict the rating of a film that has yet to be released.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Problem Description}
	When creating a film, there are many factors that attribute to the success of the film. Film producers always want to make a profit and they will not know if their film will be a 'hit' or a 'flop' until it is released to the public. Our program will utilize factors to predict the average rating a film will receive and this well represent the film's predicted success.

%-------------------------------------------------------------------------
\section{Survey}
	To see how much of an impact this project would have with the general population, we asked 50 students their opinion.\\
Q: Do you believe this project will have an impact on which movies you will watch based on the rating generated?\\ \\37 students said it would have an impact.\\
9 students said it would not impact them.\\
4 students said they did not know.

%-------------------------------------------------------------------------
\section{Plan}
	March 8th - Understand the Problem in-depth\\
	March 14th - Develop a data base for the code\\
	March 25th - Complete a base algorithm for Project\\
	March 29th - Complete Intermediate Project Report\\
	April 10th - Research ways to make algorithm more accurate\\
	April 20th - Edit algorithm to be more effective and more precise\\ 
	April 29th - Complete Final Project Presentation\\
	May 4th - Complete Final Project Report

%-------------------------------------------------------------------------

%%%%%%%%% BIBLIOGRAPHY
\begin{thebibliography}{9}
	\bibitem{latexcompanion} 
	Quader, Nahid \& Gani, Md. \& Chaki, Dipankar \& Ali, Md. 
	\textit{A Machine Learning Approach to Predict Movie Box-Office Success}. 
	Reading, Bangladesh, 2018.
	\bibitem{latexcompanion} 
	Sharda, Ramesh \& Delen, Dursun 
	\textit{Predicting box-office success of motion pictures with neural networks}. 
	Expert Systems with Applications. 30. 243-254. 10.1016/j.eswa.2005.07.018.
\end{thebibliography}

\end{document}
